---
title: "stock_picker"
output: html_notebook
---

The purpose of this file is to use evaluate stocks against some selection critiera to evaluate if the stock could be a potential buy. This is done by applying a logic that checks that some condition is fulfilled for each stock.

Set today´s date as a variable
```{r}
today <- Sys.Date()
```

Loading required packages

### Tidyquant and other

```{r, message=TRUE}
library(tidyquant) # for pulling stock quotes with tq_get()
library(zoo)       # for calculating rolling mean with rollmean()
library(tidyverse) # for plotting
# Documentation:
# https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ01-core-functions-in-tidyquant.html
```
###Pull stock info

```{r}
# Docs: https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ01-core-functions-in-tidyquant.html

# check what indexes we have in tidyquant
tq_index_options() # DOW, DOWGLOBAL, SP400, SP500, SP600

index_list <- tq_index_options()
x <- 1 # the first exchange in the list e.g "DOW"

# get quotes one index
tq_index("DOW")

index_info <- tq_index(index_list[x])
glimpse(index_info)
```
Above we have a tibble with X rows, one for each company in the index.

Next, get stock info for one company from the tibble and examine the results.
```{r}
# use tq_get()
tq_get_options()
```
We want to use "stock_prices" argument.
```{r}
tq_get("AAPL", 
       get = "stock.prices",
       from = today - 3*365,
       to = today)
```

Try if this can be done using tidyverse.
```{r}
index_info %>%
  select(symbol) %>%
  head(1) %>%
  tq_get(get = "stock.prices", 
         from = today - 3*365,
         to = today)
```

Now we want to create the criteria of selection.

- Compare MA200 with MA50
- If MA50 > MA200 then select the stock
- Set time period?

TBD

Next, try to loop over the tibble row wise for each company and collect stock info.

TBD

...
