---
title: "stock_picker"
output: html_notebook
---

The purpose of this file is to use evaluate stocks against some selection critiera to evaluate if the stock could be a potential buy. This is done by applying a logic that checks that some condition is fulfilled for each stock.

Set today´s date as a variable
```{r}
today <- Sys.Date()
```

Loading required packages

### Tidyquant and other

```{r, message=TRUE}
library(tidyquant) # for pulling stock quotes with tq_get()
library(zoo)       # for calculating rolling mean with rollmean()
library(tidyverse) # for plotting
# Documentation:
# https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ01-core-functions-in-tidyquant.html
```
###Pull stock info

```{r}
# Docs: https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ01-core-functions-in-tidyquant.html

# check what indexes we have in tidyquant
tq_index_options() # DOW, DOWGLOBAL, SP400, SP500, SP600

index_list <- tq_index_options()
x <- 1 # the first exchange in the list e.g "DOW"

# get quotes one index
tq_index("DOW")

index_info <- tq_index(index_list[x])
glimpse(index_info)
```
Above we have a tibble with X rows, one for each company in the index.

Next, get stock info for one company from the tibble and examine the results.
```{r}
# use tq_get()
tq_get_options()
```
We want to use "stock_prices" argument.
```{r}
tq_get("AAPL", 
       get = "stock.prices",
       from = today - 3*365,
       to = today)
```

Try if this can be done using tidyverse.
```{r}
df <- index_info %>%
  select(symbol) %>%
  head(1) %>% # Take the first symbol for now
  tq_get(get = "stock.prices", 
         from = today - 3*365,
         to = today)
df
```

Now we want to create the criteria of selection.

- Calculate and Compare MA200 with MA50
- If MA50 > MA200 then select the stock
- Set time period?

Calculate and compare MA200 and MA50
```{r}
# select symbol
symbol_col <- df %>%
  select(symbol)

# select date
date_col <- df %>%
  select(date)

# calculate rolling 50
roll_50 <- df %>%
  select(close) %>%
  rollmean(50,
           fill = NA,
           align = "right")

# calculate rolling 200
roll_200 <- df %>%
  select(close) %>%
  rollmean(200,
           fill = NA,
           align = "right")

# Compare the ma 50 and ma 200
df_comp <- data.frame("symbol"   = symbol_col,
                      "date"     = date_col,
                      "ma_50"    = roll_50,
                      "ma_200"   = roll_200)

names(df_comp) <- c("symbol", "date", "ma_50", "ma_200") 

# check tail
df_comp %>%
  tail()

# check logic if ma_50 >= ma_200
df_comp %>%
  filter(ma_50 >= ma_200,
         date == max(date))%>%
  select(symbol,date, ma_50, ma_200) # select the date and the max 
```

These are the stocks that we want to plot then.
These are potential buy candidates with upside momentum.


Plot the data
```{r}
# set start and end date for the plot
b1 <- as.Date(min(df$date))
b2 <- as.Date(max(df$date))

ggplot(df, aes(x = date, y = close, group = 1, col = "close")) +
  geom_line() +
  geom_line(data = df, aes(x = date, 
                           y = rollmean(close, 50, 
                                        fill = NA, 
                                        align = "right"), 
                           group = 1, 
                           col = "ma_50")) +
  geom_line(data = df, aes(x = date, 
                           y = rollmean(close, 200, 
                                        fill = NA, 
                                        align = "right"), 
                           group = 1, 
                           col = "ma_200")) +
  scale_x_date(breaks = c(b1,b2)) +
  ggtitle(paste(df[1,1], names(df)[5], " from",b1," to ",b2)) +
  xlab("date") #+
  #theme_minimal() +
  #geom_vline(xintercept = t, linetype = 2,  color = "brown", alpha = .5)
```

Next, try to loop over the tibble row wise for each company and collect stock info. The stocks that pass the selection criteria, these stocks we want to plot according to above. The rest we don´t care about.

TBD

...
