---
title: "stock_picker"
output: html_notebook
---

The purpose of this file is to use evaluate stocks against some selection criteria to evaluate if the stock could be a potential buy. This is done by applying a logic that checks that some condition is fulfilled for each stock.

Set today´s date as a variable
```{r}
today <- Sys.Date()
```

Loading required packages

### Tidyquant and other

```{r, message=FALSE}
library(tidyquant) # for pulling stock quotes with tq_get()
library(quantmod)  # for pulling DJI index. tidyquants version is incomplete
library(zoo)       # for calculating rolling mean with rollmean()
library(tidyverse) # for plotting
# Documentation:
# https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ01-core-functions-in-tidyquant.html
```

### Pull stock info

```{r}
# Docs: https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ01-core-functions-in-tidyquant.html

# check what indexes we have in tidyquant
tidyquant::tq_index_options() # DOW, DOWGLOBAL, SP400, SP500, SP600

index_list <- tidyquant::tq_index_options()
# the first exchange in the list e.g 1 = "DOW" or 4 = "SP500" (too many to plot in one session)
x <- 1 # "DOW", 30
#x <- 2 # "DOWGLOBAL", 156

# get quotes one index
index_info <- tidyquant::tq_index(index_list[x])
glimpse(index_info)
index_info
```
Above we have a tibble with X rows, one for each company in the index.

Plot the weights of company on index - Out of curiosity mostly
```{r}
#fig.width=12, fig.height=14
index_info %>%
  #arrange(-weight) %>%
  head(35) %>% # top 50 
  ggplot(aes(x = reorder(company, weight), y = weight)) +
  geom_col() +
  coord_flip() +
  xlab("Company Name") +
  ggtitle("Company List")
```
Comment: Evaluate Company List plot during each update for potential companies to excluded.
Company names to exclude: US DOLLAR and SOLVENTUM CORP. Assigned below to variable symbol_exclude.

Next, get stock info for one company from the tibble and examine the results.
```{r}
# use tq_get()
tidyquant::tq_get_options()
```
We want to use "stock_prices" argument.
```{r}
# Alt 1. Select specific stock manually! E.g "TSLA" or "DJI" for DOW index
df <- tidyquant::tq_get("DJI", # From DOWGLOBAL "ABBV" 
       get = "stock.prices",
       from = today - 4*365,
       to = today)

head(df)
```

Start by checking DJI and VIX index as reference symbols for overall market behavior.

```{r}
# Fetch historical data for the DJIA and VIX index using quantmod due to incomplete series for DJI in tidyquant. Versions used tidyquant 1.0.3, quantmod 0.4.20. These stopped working on 2024-09-15 with an HFTTP error 401.

# Create list if reference symbols for over all market behaviour
reference_symbols = list("^DJI","^VIX")

# Create the empty data frame for historical data
df <- data.frame(symbol   = character(),
                 date     = as.Date(character()),
                 open     = double(),
                 high     = double(),
                 low      = double(),
                 close    = double(),
                 adjusted = double())

# fetch historical data for each symbol
for(symbol in reference_symbols) {
  
  quantmod::getSymbols(symbol, from = today - 4*365, to = today)
  
  # Create a reference to the data object
  data_obj <- get(gsub("\\^", "", symbol))

  # Create the data frame
  df_symbol <- data.frame(date = index(data_obj), coredata(data_obj))
  
  # Set colnames similar to tidyquant
  new_colnames <- c("date","open","high","low","close","volume","adjusted")
  colnames(df_symbol) <- new_colnames
  df_symbol["symbol"] <- symbol
  
  # rearrange columns
  df_symbol <- df_symbol %>%
    dplyr::select("symbol","date","open","high","low","close","volume","adjusted")
  
  # bind symbol data frame to result data frame
  df = rbind(df, df_symbol)

}
  
# Print the first few rows of the data
head(df)
```
Check data for NA values
```{r}
# Check nbr of rows before cleaning
print(dim(df)[1])
      
na_close_cnt <- sum(is.na(df$close))
print(paste("Nbr of rows in df with col 'close' NA:", na_close_cnt))

if (na_close_cnt > 0) {
  df_clean <- na.omit(df)
  # reassign df to df_clean
  df <- df_clean
}

# Check nbr of rows after cleaning
print(dim(df)[1])
```

Calculate and compare MA200 and MA50 and plot the data to spot trends.
```{r}
# set start, break and end date for the plot
breaks <- as.Date(min(df$date)) + (0:3)*365 
breaks <- c(breaks, as.Date(max(df$date)) )

# slice data frame for symbol 1 for plotting
df_slice = df %>% 
  dplyr::filter(symbol == reference_symbols[1])

# create plot
ggplot(df_slice, aes(x = date, y = close, group = 1, col = "close")) +
  geom_line() +
  geom_line(data = df_slice, aes(x = date, 
                           y = rollmean(close, 50, 
                                        fill = NA, 
                                        align = "right"), 
                           group = 1, 
                           col = "ma_50")) +
  geom_line(data = df_slice, aes(x = date, 
                           y = rollmean(close, 200, 
                                        fill = NA, 
                                        align = "right"), 
                           group = 1, 
                           col = "ma_200")) +
  scale_x_date(breaks = breaks) +
  ggtitle(paste(df_slice[1,1], names(df_slice)[6], " from", breaks[1]," to ", breaks[length(breaks)]) ) +
  xlab("date") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
  #geom_vline(xintercept = t, linetype = 2,  color = "brown", alpha = .5)


# slice data frame for symbol 2 for plotting
df_slice = df %>% 
  dplyr::filter(symbol == reference_symbols[2])

# create plot
ggplot(df_slice, aes(x = date, y = close, group = 1, col = "close")) +
  geom_line() +
  geom_line(data = df_slice, aes(x = date, 
                           y = rollmean(close, 50, 
                                        fill = NA, 
                                        align = "right"), 
                           group = 1, 
                           col = "ma_50")) +
  geom_line(data = df_slice, aes(x = date, 
                           y = rollmean(close, 200, 
                                        fill = NA, 
                                        align = "right"), 
                           group = 1, 
                           col = "ma_200")) +
  scale_x_date(breaks = breaks) +
  ggtitle(paste(df_slice[1,1], names(df_slice)[6], " from", breaks[1]," to ", breaks[length(breaks)]) ) +
  xlab("date") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
  #geom_vline(xintercept = t, linetype = 2,  color = "brown", alpha = .5)
```

Now we can start the analysis on stock symbol level for the selected index.

### Loop Construct ###

```{r}
# check unique values in index_info
lapply(index_info, function(x) {length(unique(x))})
```
Next, we collect the symbols from above into a tibble and loop row wise for each company and collect stock info. The stocks that pass the selection criteria, these stocks we want to plot according to above. We could add a proper filter to capture date that is closed to today. The rest of the stocks we don´t care about.

```{r}

#i <- "HD"

# create two empty df for the results
df_comp_results <- data.frame("symbol" = as.character(),
                              "date"   = as.Date(x = integer(0), origin = "1970-01-01"),
                              "close"  = as.numeric(),
                              "ma_50"  = as.numeric(),
                              "ma_200" = as.numeric())

df_results <- data.frame("symbol" = as.character(),
                         "date"   = as.Date(x = integer(0), origin = "1970-01-01"),
                         "close"  = as.numeric(),
                         "ma_50"  = as.numeric(),
                         "ma_200" = as.numeric())

## Initialize a vector to store symbols that generate warnings
warning_symbols <- c()

# loop over each stock in the index_info
for (i in unique(index_info$symbol)) {
  
  ## Data collection step fails sometimes, skip symbol if it generates warning/error while fetching data
  skip_to_next <- FALSE
  error_vec <- as.vector(c())
  
  tryCatch(
    # segment the data
    {df <- index_info %>%
      dplyr::filter(symbol == i) %>%
      dplyr::select(symbol) %>%
      head(1) %>% 
      tidyquant::tq_get(get = "stock.prices",
             from = today - 3*365,
             to = today)
    }, warning = function(w) {
      
      skip_to_next <<- TRUE
      warning_symbols <<- c(warning_symbols, i) # add the symbol to the warning symbols vector
      #cat(" ",i, " ") # print symbol
      cat("Warning: Error in data collection for symbol", i, "\n") # print warning
      
    }, error = function(e) {
      skip_to_next <<- TRUE
      cat("Error: Data collection failed for symbol", i, "\n") # print error
      })
  
  if(skip_to_next) { error_vec <<- append(error_vec, i) ; next }

  ## calculate moving averages

  # select symbol
  symbol_col <- df %>%
    dplyr::select(symbol)

  # select date
  date_col <- df %>%
    dplyr::select(date)
  
  # select close
  close <- df %>%
    dplyr::select(close)

  # calculate rolling 50
  roll_50 <- df %>%
    dplyr::select(close) %>%
    zoo::rollmean(50,
             fill = NA,
             align = "right")

  # calculate rolling 200
  roll_200 <- df %>%
    dplyr::select(close) %>%
    zoo::rollmean(200,
             fill = NA,
             align = "right")

  # Compare the ma 50 and ma 200
  df_comp <- data.frame("symbol"   = symbol_col,
                        "date"     = date_col,
                        "close"    = close,
                        "ma_50"    = roll_50,
                        "ma_200"   = roll_200)

  names(df_comp) <- c("symbol", "date", "close", "ma_50", "ma_200") 

  # check logic if ma_50 >= ma_200
  df_comp_summary <- df_comp %>% 
    dplyr::filter(ma_50 >= ma_200,
           date == max(date))%>%
    dplyr::select(symbol,date, close, ma_50, ma_200) # select the date and the max 

  # bind results
  df_comp_results <- rbind(df_comp_results, df_comp)   # all rows per symbol  
  df_results      <- rbind(df_results,df_comp_summary) # one row per symbol
}

# clean up
rm(symbol_col,date_col,roll_50,roll_200,df_comp,df_comp_summary)

# store the df locally
#write.csv2(df_comp, file="df_comp.csv")
cat("Number of symbols in total",nrow(index_info[1]),"\n")
cat("Number of symbols with Warning",length(warning_symbols),"\n")
rm(warning_symbols)
```
Exclude US Dollar (-) and (SOLV) based on Company List plot above.
```{r}
# Print nbr of unique symbols before exclusion
print(length(unique(df_results$symbol)) )

# Symbols to exclude
symbol_exclude <- c("-","SOLV")

# Check if symbols are included in the df_results and replace them
if(any(df_results$symbol %in% symbol_exclude)) {
  df_results <- df_results %>%
    dplyr::filter(!symbol %in% symbol_exclude)
}

# Print nbr of unique symbols after exclusion
print(length(unique(df_results$symbol)) )
```


Create plots
```{r}
# version 1

# plot only the symbols that are in the df_results
df_plot <- df_comp_results %>%
  dplyr::filter(symbol %in% unique(df_results$symbol))

# set start, break and end date for the plot
breaks <- as.Date(min(df$date)) + (0:3)*365 
breaks <- c(breaks, as.Date(max(df$date)) )

df_plot %>%
  ggplot(aes(x = date, y = close, group = 1, col = "close")) +
  geom_line() +
  geom_line(data = df_plot, aes(x = date,
                                y = ma_50,
                                group = 1,
                                col = "ma_50")) +
  geom_line(data = df_plot, aes(x = date,
                                y = ma_200,
                                group = 1,
                                col = "ma_200")) +
  scale_x_date(breaks = breaks) +
  ggtitle(paste("By stock symbol the close, ma_200, ma_50"," from", breaks[1]," to ", breaks[length(breaks)]) ) +
  xlab("date") +
  theme(axis.text.x = element_text(size=8.5)) +
  facet_wrap(~symbol, scales = "free")

```

```{r}
# version 2

# plot only the symbols that are in the df_results
df_plot <- df_comp_results %>%
  dplyr::filter(symbol %in% unique(df_results$symbol))

# set start, break and end date for the plot
breaks <- as.Date(min(df$date)) + (0:3)*365 
breaks <- c(breaks, as.Date(max(df$date)) )

df_plot %>%
  ggplot(aes(x = date, y = close, group = 1, col = "close")) +
  geom_line() +
  geom_line(data = df_plot, aes(x = date,
                                y = ma_50,
                                group = 1,
                                col = "ma_50")) +
  geom_line(data = df_plot, aes(x = date,
                                y = ma_200,
                                group = 1,
                                col = "ma_200")) +
  scale_x_date(breaks = breaks) +
  ggtitle(paste("By stock symbol the close, ma_200, ma_50"," from", breaks[1]," to ", breaks[length(breaks)]) ) +
  xlab("date") +
  theme(axis.text.x = element_text(size=8.5)) +
  facet_wrap(~symbol, scales = "free")

```

The above plot contains the stocks that fulfill our selection criteria of ma_50 above ma_200.
Next, add what point in time the rule should apply.  
Comment to above plots: There was a major drop in stock prices globally in third week of Jan 2022. Due to Ukraine crisis and Omikron. Several stocks passed the death-cross AXP, CRM, GS, JPM while MRK, TRV are close to it on 2022-02-13.
GS, JPM passed death cross while AXP, MRK are still above on 2022-02-23.
2022-02-24 Russia invaded Ukraine. 
2022-08-28. 8 stocks above dc. MRK, TRV is out and MCD is in.
...
2022-10-27. 5 stocks above dc. AMGN is in again after ath.
2022-11-29. 16 stocks above dc. HON, NFLX, TRV, WMT is in. NEE is out.
2022-12-19. 29 stocks above dc. BA, DD, HD, MDLZ, RTX, SPG in.
2022-12-31. 35 stocks above dc. BAC, CSCO, JNJ, NEE, V, WMB in.
2023-01-15. 20 stocks above dc. KO, NKE, PG. Switched back to DOW 30 frow DOW GLOBAL
2023-02-03. 20 stocks above dc (47 from DOW GLOBAL). AXP in. UNH, WBA out. Date was biggest stock increase YTD in OMXS. 
2023-02-19. 20 stocks above dc. JPM out.
2023-03-05. 19 stocks above dc. KO out.
2023-03-12. 19 stocks above dc. AMGN out. DIS in. 
2023-03-19. 18 stocks above dc. CRM in. GS, IBM out. 
2023-03-26. 20 stocks above dc. AAPL, GS, MSFT in. PG out. MSFT revealed gpt4 powered Office 365 copilot and github copilot x.
2023-04-10. 20 stocks above dc. Same status as previous update.
2023-04-16. 17 stocks above dc. CVX, DIS, HD, HON out. PG in.
2023-04-23. 16 stocks above dc. GS out. 
2023-05-01. 17 stocks above dc. KO in. 
2023-05-03. 16 stocks above dc. TRV out.
2023-05-15. 17 stocks above dc. INTC in.
2023-05-28. 16 stocks above dc. CAT out.
2023-06-18. 16 stocks above dc. Same status, increased in MSFT.
2023-07-09. 16 stocks above dc. CAT in. DOW out.
2023-07-17. 16 stocks above dc. HON in. NKE out.
2023-08-13. 16 stocks above dc. HD, IBM in. HON, KO out.
2023-08-21. 16 stocks above dc. JNJ in. MRK out.
2023-08-26. 16 stocks above dc. No change.
2023-09-07. 17 stocks above dc. DOW in.
2023-09-17. 18 stocks above dc. AMGN in. 
2023-09-27. 17 stocks above dc. AXP, DOW out. UNH in.
2023-10-25. 15 stocks above dc. CVX in. BA, JNJ, MCD out.
2023-11-05. 14 stocks above dc. HD out.
2023-11-19. 13 stocks above dc. CVX out.
2023-11-27. 12 stocks above dc. PG out.
2023-12-26. 16 stocks above dc. BA, GS, HD, TRV, VZ in. CSCO out.
2023-12-31. 18 stocks above dc. AXP, NKE in.
2024-01-07. 20 stocks above dc. DIS, HON in.
2024-01-28. 24 stocks above dc. DOW, MCD, MMM, MRK in.
2024-02-04. 24 stocks above dc. Same status as previous update. Into DIS.
2024-02-09. 24 stocks above dc. No change.
2024-02-15. 25 stocks above dc. KO in.
2024-02-24. 26 stocks above dc. PG in. Increased in MCD.
2024-03-03. 26 stocks above dc. AMZN in. NKE out.
2024-03-08. 24 stocks above dc. BA, MMM out.
2024-03-17. 24 stocks above dc. JNJ in. AAPL out.
2024-03-22. 22 stocks above dc. JNJ, UNH out. DJI at ath, VIX extremely low.
2024-04-05. 22 stocks above dc. Same status as previous update. VIX is up. Increased in MCD.
2024-04-12. 22 stocks above dc. same status. VIX is up. Iran bombed Israel on 2024-04-13. Exit DIS.
2024-04-19. 24 stocks above dc. CVX, MMM in. DJI is down. VIX is up. Iran did not respond again. Increased in Meta.
2024-04-26. 26 stocks above dc. Same status. VIX down to 14.
2024-05-03. 22 stocks above dc. INTC, MCD out. DJI is up. VIX down to 7. Into HD.
2024-05-14. 22 stocks above dc. Same status. VIX is down. DJI is up.
2024-05-24. 22 stocks above dc. Same status. DJI is up to 39069, VIX down 12.
2024-06-09. 22 stocks above dc. Same status. DJI is down to 38798, VIX is same at 12.
2024-06-28. 23 stocks above dc. AAPL in. DJI is up to 39119, VIX is same at 12.
2024-07-07. 23 stocks above dc. Same status as previous update. DJI is up to 39376, VIX is similar at 12. Increase in MMM.
2024-08-03. 21 stocks above dc. UNH in, CRM, DIS, DOW out.  DJI up to 39737, VIX up to 23.
2024-08-11. 20 stocks above dc. VZ out. DJI down to 39497, VIX was up 38 dropped to 20 during the week.
2024-08-23. 19 stocks above dc. CVX is out. DJI is up 41175, VIX down 17.
2024-08-30. 20 stocks above dc. JNJ in. DJI is up 41563, VIX down 15.
2024-09-13. 19 stocks above dc. MRK is out. DJI is down 41393, VIX up 17. tidyquant lib update needed.
2024-09-27. 21 stocks above dc. CSCO, MCD in. DJI is up 42175, VIX down 15.
2024-10-13. 22 stocks above dc. V is in. DJI is up 42863, VIX up 20.
2024-10-25. 22 stocks above dc. Same status. DJI is down 42114, VIX on 20.
2024-11-08. 24 stocks above dc. CRM, NVDA, SHW in. MSFT out. DJI is up 43989, VIX down 15. Trump won US president election.
2024-11-22. 25 stocks above dc. MSFT in. DJI up 44296, VIX same 15.
2024-12-06. 26 stocks above dc. CVX, DIS in, MSFT out. DJI up 44642, VIX down 13.
2024-12-15. 26 stocks above dc. AMGN is out, MSFT in. DJI down 43828, VIX up 14.
2024-12-20. 25 stocks above dc. KO out. DJI is down 42840, VIX is up 18.
2025-01-06. 23 stocks above dc. CVX, JNJ is out. DJI down 42732, VIX down 16.
2025-01-24. 23 stocks above dc. CVX in, VZ is out. DJI up 44424, VIX down 15.
2025-01-31. 22 stocks above dc. UNH out. DJI up 44544, VIX up 16.
2025-02-15. 21 stocks above dc. BA in. CVX, PG out. DJI up 44546, VIX down 15.
2025-03-09. 21 stocks above dc. CVX in, MSFT out. DJI down 42801, VIX up 23. Trump US tariff policy.
2025-03-26. 20 stocks above dc. JNJ, KO in. CAT, NVDA, SHW out. DJI down to 42587, VIX down 17.
2025-03-31. 20 stocks above dc. HON out, VZ in. DJI down to 41583, VIX up 22.
2025-04-04. 20 stocks above dc. HD out, PG in. DJI plunge to 38315, VIX up 45 on 4 year high. Trump US tariffs per country.
2025-04-13. 18 stocks above dc. AAPL, PG is out. DJI surge to 40212, VIX down to 37. Trump pauses US tariffs for 90 days except for CN.
2025-04-25. 14 stocks above dc. AMZN, AXP, CRM, DIS out. DJI down to 40113, VIX down to 25.
2025-05-04. 12 stocks above dc. CVX, GS out. DJI up to 41318, VIX down to 23. 
2025-05-09. 12 stocks above dc. Same status as previous update. DJI down to 41249, VIX down to 22.
2025-05-18. 12 stocks above dc. Same status as prev update. DJI up to 42654, VIX down 17.
2025-05-27. 11 stocks above dc. JNJ out. DJI down to 41603, VIX up to 22.
2025-06-22. 13 stocks above dc. DIS, GS, MSFT in. VZ out. DJI up to 42207, VIX down to 21. Trump bombed Iran on weekend after close.
2025-07-12. 18 stocks above dc. AMZN, AXP, HON, NVDA, VZ in. DJI up to 44371, VIX down to 16.
2025-08-10. 20 stocks above dc. AMGN, CAT, JNJ in. MCD out. DJI down to 44175, VIX down 15.
2025-11-09. 20 stocks above dc. No comparison due to new laptop. DJI up to 46897, VIX up 19.
2025-11-16. 20 stocks above dc. AMGN in. NKE out. DJI up to 47147, VIX up 20.
2025-11-24. 20 stocks above dc. No change. DJI down to 46245, VIX up 23.
2025-11-30. 20 stocks above dc. Same status. DJI up to 47716, VIX down to 16.

```{r}
# check the selected stocks
index_info %>%
  dplyr::filter(symbol %in% (df_results$symbol)) %>%
  dplyr::arrange(symbol)
```
```{r}
# Adding Shiny app
library(shiny)

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      checkboxGroupInput("symbols", "Select symbols to plot:", 
                         choices = sort(unique(df_results$symbol)),
                         selected = unique(df_results$symbol)) # Default selection all symbols
    ),
    mainPanel(
      plotOutput("plot")
    )
  )
)

server <- function(input, output) {
  output$plot <- renderPlot({
    # Filter df_comp_results to only include rows where the symbol column value is present in df_results$symbol and selected by the user
    df_plot <- df_comp_results %>%
      dplyr::filter(symbol %in% input$symbols)
    
    # Set start, break, and end date for the plot
    date_breaks <- as.Date(min(df_comp_results$date)) + (0:3)*365
    date_breaks <- c(date_breaks, as.Date(max(df$date)) )
    # 
    # # # Check if df is empty
    # if (nrow(df) > 0) {
    #   # Set start, break, and end date for the plot
    #   date_breaks <- as.Date(min(df$date)) + (0:3)*365 
    #   date_breaks <- c(date_breaks, as.Date(max(df$date)) )
    # } else {
    #   # Set date_breaks to an empty vector
    #   date_breaks <- c()
    # }
    
    # Create the plot
    df_plot %>%
      ggplot(aes(x = date, y = close, group = 1, col = "close")) +
      geom_line() +
      geom_line(data = df_plot, aes(x = date,
                                    y = ma_50,
                                    group = 1,
                                    col = "ma_50")) +
      geom_line(data = df_plot, aes(x = date,
                                    y = ma_200,
                                    group = 1,
                                    col = "ma_200")) +
      scale_x_date(breaks = date_breaks) +
      ggtitle(paste("By stock symbol the close, ma_200, ma_50", " from", 
                    date_breaks[1], " to ", 
                    date_breaks[length(date_breaks)])) +
      xlab("date") +
      theme(axis.text.x = element_text(size=8.5)) +
      facet_wrap(~symbol, scales = "free")
  })
}

shinyApp(ui, server)

```

