---
title: "trading_fil"
output: html_notebook
---

This notebook contains stock quotes.

```{r}
library(tidyquant)
library(XLConnect)
library(rJava)
library(XLConnectJars) # Need newer Java version installed!
```

START HERE!

Set todays date as a variable
```{r}
today <- Sys.Date()
```


### Using tidyquant package ###

The tidyquant package is focused on retrieving, manipulating, and scaling financial data analysis in the easiest way possible.

```{r, message=TRUE}
library(tidyquant) # for pulling stock quotes with tq_get()
library(zoo)       # for calculating rolling mean with rollmean()

# Documentation:
# https://cran.r-project.org/web/packages/tidyquant/vignettes/TQ01-core-functions-in-tidyquant.html
```


Plot stock data 1
```{r, fig.width=9}
# Pull stock data using tidyquant, set stock to the quote!
stock <- "AAPL" 
df <- tq_get(stock, get = "stock.prices", 
                from = "2016-01-01", to = today)

# Transaction dates
# t <- as.Date("2018-12-10") # SOLD/BUY - brown/black dashed

b1 <- as.Date(min(df$date))
b2 <- as.Date(max(df$date))

ggplot(df, aes(x = date, y = close, group = 1, col = "close")) +
  geom_line() +
  geom_line(data = df, aes(x = date, y = rollmean(close, 50, fill = NA, align = "right"), 
                           group = 1, col = "ma_50")) +
  geom_line(data = df, aes(x = date, y = rollmean(close, 200, fill = NA, align = "right"), 
                           group = 1, col = "ma_200")) +
  scale_x_date(breaks = c(b1,b2)) +
  ggtitle(paste(stock," from",b1," to ",b2)) +
  xlab("date")
  #geom_vline(xintercept = t, linetype = 2,  color = "brown", alpha = .5)
```

Plot stock data 2
```{r, fig.width=9}
# Pull stock data using tidyquant, set stock to the quote!
stock <- "MCD" 
df <- tq_get(stock, get = "stock.prices", 
                from = "2016-01-01", to = today)

# Transaction dates
t <- as.Date("2018-08-30") # BUY - black dashed

b1 <- as.Date(min(df$date))
b2 <- as.Date(max(df$date))

ggplot(df, aes(x = date, y = close, group = 1, col = "close")) +
  geom_line() +
  geom_line(data = df, aes(x = date, y = rollmean(close, 50, fill = NA, align = "right"), 
                           group = 1, col = "ma_50")) +
  geom_line(data = df, aes(x = date, y = rollmean(close, 200, fill = NA, align = "right"), 
                           group = 1, col = "ma_200")) +
  scale_x_date(breaks = c(b1,b2)) +
  ggtitle(paste(stock," from",b1," to ",b2)) +
  xlab("date") +
  geom_vline(xintercept = t, linetype = 2,  color = "black", alpha = .5)
```

Plot stock data 3
```{r, fig.width=9}
# Pull stock data using tidyquant, set stock to the quote!
stock <- "SNE" 
df <- tq_get(stock, get = "stock.prices", 
                from = "2016-01-01", to = today)

# Transaction dates
t <- as.Date("2018-12-10") # SOLD - brown solid

b1 <- as.Date(min(df$date))
b2 <- as.Date(max(df$date))

ggplot(df, aes(x = date, y = close, group = 1, col = "close")) +
  geom_line() +
  geom_line(data = df, aes(x = date, y = rollmean(close, 50, fill = NA, align = "right"), 
                           group = 1, col = "ma_50")) +
  geom_line(data = df, aes(x = date, y = rollmean(close, 200, fill = NA, align = "right"), 
                           group = 1, col = "ma_200")) +
  scale_x_date(breaks = c(b1,b2)) +
  ggtitle(paste(stock," from",b1," to ",b2)) +
  xlab("date") +
  geom_vline(xintercept = t, linetype = 1,  color = "brown", alpha = .5)
```

Plot stock data 4
```{r, fig.width=9}
# Pull stock data using tidyquant, set stock to the quote!
stock <- "IBM" 
df <- tq_get(stock, get = "stock.prices", 
                from = "2016-01-01", to = today)

# Transaction dates
t <- as.Date("2018-12-10") # SOLD - brown solid

b1 <- as.Date(min(df$date))
b2 <- as.Date(max(df$date))

ggplot(df, aes(x = date, y = close, group = 1, col = "close")) +
  geom_line() +
  geom_line(data = df, aes(x = date, y = rollmean(close, 50, fill = NA, align = "right"), 
                           group = 1, col = "ma_50")) +
  geom_line(data = df, aes(x = date, y = rollmean(close, 200, fill = NA, align = "right"), 
                           group = 1, col = "ma_200")) +
  scale_x_date(breaks = c(b1,b2)) +
  ggtitle(paste(stock," from",b1," to ",b2)) +
  xlab("date") +
  geom_vline(xintercept = t, linetype = 1,  color = "brown", alpha = .5)
```

End of stock quotes!




```{r}
eur_usd <- tq_get("EUR/USD", 
                  get = "exchange.rates", 

                  from = Sys.Date() - lubridate::days(10))
eur_usd
df <- eur_usd

# graph below doesnt really work
ggplot(df, aes(x = as.factor(date), y = exchange.rate, group = 1, col = "exchange.rate")) +
  geom_line() +
  geom_line(data = df, aes(x = as.factor(date), y = rollmean(close, 50, fill = NA, align = "right"), 
                           group = 1, col = "ma_50")) +
  geom_line(data = df, aes(x = as.factor(date), y = rollmean(close, 200, fill = NA, align = "right"), 
                           group = 1, col = "ma_200")) +
  scale_x_discrete(breaks = c(b1,b2)) +
  ggtitle(paste("eur_usd"," from",b1," to ",b2)) +
  xlab("date")

```




```{r}
df_50  <- rollmean(df$close, 50, fill = NA)
plot(rollmax(df$close, 50))
plot(df_50)
df_200 <- rollmean(df$close, 200, fill = NA)
plot(df_200)

```


```{r}
tq_transmute_fun_options() # Check all functions of tidyquant packages
```



Plot stock index data
```{r, fig.width=9}

# Get the available index
tq_index_options()

# Get available sources
tq_get_options()

# Get all stocks in a stock exchange
nyse_stocklist <- tq_exchange("NYSE")
head(nyse_stocklist)

nyse_stocklist %>%
  group_by(sector) %>%
  summarise(nbr_companies = n()) %>%
  arrange(-nbr_companies)

tq_transmute_fun_options() # Check all functions of tidyquant packages

# Source for more: https://www.business-science.io/
```

Below produces and error. Java version issue?
```{r}
# Pull index data using tidyquant
df <- tq_index("SP500")
# Above should load in 1.2 million rows of SP500 stocks

# Below converts all of SP500 into percent monthly percent units for all stocks
sp_500 %>%
  group_by(symbol) %>%
  tq_transmute(adjusted, mutate_fun = monthlyReturn)
```



```{r}
day1 <- as.Date("2018-11-30")
day1 <- as.Date("2018-12-02")

if(today > day1) {
  print("Idag är det en dag efter:"); day1
} else {
  print("Idag är det en dag före") ; day1
}
rm(today); rm(day1)
```




TBD


